---
title: "Assignment"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
# Assignment 1

**Collaborators: Lorem Ipsum. **

This assignment is due on Canvas on Monday 9/20 before class, at 10:15 am. Include the name of anyone with whom you collaborated at the top of the assignment.


### Problem 1 

Install the datasets package on the console below using `install.packages("datasets")`. Now load the library.

```{r}
#install.packages("datasets")
library(datasets)
```
_Answer_: Line51 install the package(I#it out because it only need to be done once). Line52 load the library.

Load the USArrests dataset and rename it `dat`. Note that this dataset comes with R, in the package datasets, so there's no need to load data from your computer. Why is it useful to rename the dataset?

```{r}
# This line load the USArrests dataset and rename it `dat`
dat <- USArrests
```

_Answer_: It is important to rename the dataset for the following reasons: 1. It save time typing a long name. 2. It avoid contaminating the data so that the data is replicable.

### Problem 2

Use this command to make the state names into a new variable called State. 

```{r, eval=TRUE}
dat$state <- tolower(rownames(USArrests))
```

This dataset has the state names as row names, so we just want to make them into a new variable. We also make them all lower case, because that will help us draw a map later - the map function requires the states to be lower case.


List the variables contained in the dataset `USArrests`.

```{r}
# I think both of them work as they produce the same results but with different sequences.
names(dat)
ls(dat)
```

Answer: "Assault", "Murder", "Rape", "state", and "UrbanPop". 

### Problem 3 

What type of variable (from the DVB chapter) is `Murder`? 

Answer: Quantitative variable

What R Type of variable is it?

Answer: Numeric(as indicated in the Format part of the description of the dataset)


### Problem 4

What information is contained in this dataset, in general? What do the numbers mean? 

Answer: The dataset contains the statistic of the violent crime rate of 3 different kinds of crime in the 50 US States in 1973. It also contains the percentage of urban population in these states. The number means the number of arrests per 100000 people for murder, rape, and assault. The number also means percentage urban population for UrbanPop.

### Problem 5 

Draw a histogram of `Murder` with proper labels and title.

```{r}
hist(dat$Murder, main="US Murder", xlab="Murder/100000 residents", ylab="States")
```

### Problem 6

Please summarize `Murder` quantitatively. What are its mean and median? What is the difference between mean and median? What is a quartile, and why do you think R gives you the 1st Qu. and 3rd Qu.?

```{r}
summary(dat$Murder)
```

Answer: The Mean is 7.788 and the Medium 7.250. THe difference between mean and median is 0.538. A quartile is one of the four parts that the data is divided into, and ithe data must be arranged from smallest to largest. R give me 1st Qu. and 3rd Qu. becasue it provides me information of the distribution and the shape of the data.

### Problem 7

Repeat the same steps you followed for `Murder`, for the variables `Assault` and `Rape`. Now plot all three histograms toghether. You can do this by using the command `par(mfrow=c(3,1))` and then plotting each of the three. 

```{r, echo = TRUE, fig.width = 5, fig.height = 8}
par(mfrow=c(3,1))
hist(dat$Murder, main="US Murder", xlab="Murder/100000 residents", ylab="States")

hist(dat$Assault, main="US Assault", xlab="Assault/100000 residents", ylab="States")

hist(dat$Rape, main="US Rape", xlab="Rape/100000 residents", ylab="States")
```

What does the command par do, in your own words (you can look this up by asking R `?par`)?

Answer: The Command par set the graphical parameters for the histogram that I just plotted. It set the graph to be draw in a three row and one column setting.

What can you learn from plotting the histograms together?

Answer:We can compare the shape of the histograms to find the difference of the overall trend. We can also compare the max and min more visually. We can also have a direct representation that is more clear than a chart with numbers.

### Problem 8

In the console below (not in text), type `install.packages("maps")` and press Enter, and then type `install.packages("ggplot2")` and press Enter. This will install the packages so you can load the libraries.

Run this code:

```{r, eval = TRUE, fig.width = 7.5, fig.height = 4}
#install.packages("maps")
#install.packages("ggplot2")
library('maps') 
library('ggplot2') 

ggplot(dat, aes(map_id=state, fill=Murder)) + 
  geom_map(map=map_data("state")) + 
  expand_limits(x=map_data("state")$long, y=map_data("state")$lat)
```

What does this code do? Explain what each line is doing.

Answer: The first line construct an aesthetic mapping from the dataset "dat" with the map id being state and each state is filled with the data "Murder".The second assign map data of variable "state" to the annotation of geom_map. The next two lines expand the plot's limit using the data from the variable "state" for its x and y axis.
$$\\[2in]$$
